### 2016-05-31 w-wires/paper_gerasimovda.tex
Updated paper content, supplementary numeric evaluation

$s(k)$ has countable number of zeros, all with $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, let's define $Z = \atanh \frac{2 W}{W^2 + 1}$.

@@

\begin{align*}
s_1(x + \iu y)
 &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}} && \text{(since $\cosh y \ge 1$)}\\
 &= \abs{\frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}}
\end{align*}

Note that now $s_1(k)$ has zeroes along the line $\Im k = Z = \atanh \frac{2 W}{W^2 + 1}$, which means $\ln s_1(k)$ will have continuous number of singularities along this line. However, we'll show that the function is still integrable.

@@

\todo{make the formula bigger}
\[
s_1(x + \iu y)
 = \begin{cases}
 \frac{\frac{2 W}{W^2 + 1} - \tanh y}{\tanh y + \frac{2 W}{W^2 + 1}}, & 0 \le y \le Z \\
 \frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}, & y > Z 
 \end{cases}
\]

@@

\subsubsection*{Case 1: $0 \le y \le Z$}
Since denominator $\tanh y + \frac{2 W}{W^2 + 1}$ only increases as $0 \le y \le Z$, we can replace it with its maximum value $\tanh Z + \frac{2 W}{W^2 + 1} = \frac{4 W}{W^2 + 1}$, thus getting estimate $s_2$:

\[
s_2(x + \iu y) = \frac{\frac{2 W}{W^2 + 1} - \tanh y}{\frac{4 W}{W^2 + 1}} = \frac{1}{2} - \frac{W^2 + 1}{4 W} \tanh y \le s_1(x + \iu y)
\]

@@

\[
l(k) =
\begin{cases}
1 \\
2 \\
3 
\end{cases}
\]

>>>>

$s(k)$ has countable number of zeros, all with $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, let's define $V = \frac{2 W}{W^2 + 1}$, $Z = \atanh V$.

@@

\begin{align*}
s_1(x + \iu y)
 &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}} && \text{(since $\cosh y \ge 1$)}\\
 &= \abs{\frac{\tanh y - V}{\tanh y + V}}
\end{align*}

Note that now $s_1(k)$ has zeroes along the line $\Im k = Z$, which means $\ln s_1(k)$ will have continuous number of singularities along this line. However, we'll show that the function is still integrable.

@@

\todo{make the formula bigger}
\[
s_1(x + \iu y)
 = \begin{cases}
 \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
 \frac{\tanh y - V}{\tanh y + V}, & y > Z 
 \end{cases}
\]

@@

\subsubsection*{Case 1: $0 \le y \le Z$}
We will estimate the function from below by a piecewise function containing of two pieces. We do that by noticing that the function is convex on $0 \le y \le Z$ and can be approximated from below with its first derivative at $0$ and at $Z$. 
\todo{this step is necessary because we have to $\ln f(z)$ is zero in vicinity of 0}

\[
f(y) = 
\begin{cases}
s_1'(0) y + 1   &, 0 \le y < Z_0  \\
s_1'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
=
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\]

Since denominator $\tanh y + V$ only increases as $0 \le y \le Z$, we can replace it with its maximum value $\tanh Z + V = 2 V$, thus getting estimate $s_2$:

\[
s_2(x + \iu y) = \frac{V - \tanh y}{2 V} = \frac{1}{2} - \frac{1}{2 V} \tanh y \le s_1(x + \iu y)
\]

@@

\[
l(x + \iu y) =
\begin{cases}
 \\
s_2'(Z)(y - Z)                       &, Z_0 < y \le Z \\
\frac{s_1(C + R)}{C + R - Z} (y - Z) &, y > Z
\end{cases}
\]
